---
title: "semester_reort"
output: html_document
date: "2023-11-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Semester Report 
This is a Semester Report！
Data source: "Spotted Handfish (Brachionichthys hirsutus) - GPS Underwater Visual Census - 2014-2022 repeated population surveys"


Introduction

  Spotted handfish (Brachionichthys hirsutus), a benthic species that is endemic to Tasmania (south-eastern Australia) with a food diet consisted mainly of crustaceans(shirmps), polycheate worms and small shells. 
  Since its main food source is shrimp, whether the size distribution of shrimps due to age (juveniles in shallow water and adults in deeper water) affect the distribution of their predator, i.e. Spotted handfish drew my attention.
  Hence, according to the raw data, a hypothesis was formed : "Adults/larger individuals tend to inhabit deeper water in comparison to juveniles/smaller individuals" 
To test whether this hypothesis stands true and that different size variations of the Spotted Handfish do prefer different depth of water, perhaps due to variations in food size, evaluation of the raw data using functions from the program R is demonstrated below.

```{r}
library('tidyverse')
```

```{r}
library(maptools)
library (sp)
library(raster)
library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)
library(rgbif)
library(mapr) 
library(marmap)
library(leaflet)
```

```{r}
data(wrld_simpl) 
plot(wrld_simpl,xlim=c(100,170),ylim=c(-40,-40),col='#D2B48C',bg='lightblue')
text(158, -35, 'Australia')
text(150, -45, 'Tasmania')
```


## Methods
```{r handfish}
library("readr")
read.csv("handfish.csv")
handfish <- read.csv("handfish.csv")
view(handfish)
```

# Single out the data of choice
```{r}
handfish$Fish_Length_mm
```

```{r}
handfish$Sighted_Depth_m
```

# Transform the raw data into a more organized table.
```{r}
handfishdata <- as_tibble(handfish)
handfishdata
```
# Select the 2 columns related to the hypothesis by piping handfishdata into selecting "Fish_Length_mm" and "Sighted_Depth_m".
```{r}
handfishdata <- handfishdata %>% dplyr::select(Fish_Length_mm, Sighted_Depth_m)
print(handfishdata)
```

  Adult Spotted handfish are typically 70~90-mm TL (Last et al. 2007), so we would categorize fish with a TL of 70mm or above as adults, whereas those smaller as juveniles.
# handfishdata2 = A new column specifically for Juvenile identification.
```{r}
handfishdata2 <- mutate(handfishdata, Juvenile = Fish_Length_mm < 70 )
handfishdata2
```

  Here we use the arrange function on "Fish-Length_mm" to get an idea on the correlation between Length and Depth.
# handfishdata3 = Ascending Fish_Length_mm
```{r}
handfishdata3 <- arrange(handfishdata2, Fish_Length_mm)
handfishdata3
```

## The result seemed random.
  Assuming juveniles do prefer a more shallow water, they should be found less frequently in deeper environments.We will use the arrange function to organize the "Sighted_Depth_m" in an ascending order.
# handfishdata4 = Correlation between Sighted_Depth_m and Juvenile
```{r}
handfishdata4 <- arrange(handfishdata2, Sighted_Depth_m)
handfishdata4
```
  From handfishdata4, we can briefly summarize that the hypothesis of positive correlation between Fish_Length_mm and Sighted_Depth_m is invalid, as handfishdata4 showned a result of random distribution of different fish sizes.

## Here we group the Juvenile(FAlSE = Adults, TRUE = Juveniles) to get the mean size of both categories.
```{r}
handfishdata2  %>% group_by(Juvenile) %>% summarise(Mean.Length = mean(Fish_Length_mm))
```

  Here I plot the data to see "Fish_Length_mm" and "Sighted_Depth_m" independantly.
# Plotting both "handfishdata3 and 4".
```{r}
plot(handfishdata3$Fish_Length_mm)
```

```{r}
plot(handfishdata4$Sighted_Depth_m)
```

  Now I combine the 2 variables to see the correlation of "Fish_Length_mm" and "Sighted_Depth_m" in graphic.
## Plotting "handfishdata2", setting the x-axis = "Fish length (mm)" and y=axis = "Sighted depth (m)" with the corresponding title.

```{r}
plot(Sighted_Depth_m ~ Fish_Length_mm, data = handfishdata2,
     xlab = 'Fish length (mm)', 
     ylab = 'Sighted depth (m)',
     main = 'Fish length & sighted depth of handfish')
```

  We can see that the correlation between size and depth is extremely weak as the adults and juveniles are dominantly distributed between 6m ~ 12m deep water, with the individuals sighted at 2m being full grown adults.

  Although failing to prove the hypothesis(as it may seem), we can still make our graph more...pleasing and festive :), nah just kidding, we can differentiate juveniles from adult by giving them separate colors to make the plot more easy to comprehend. 
# Use ifelse function to define color on adults and juveniles.
```{r}
col.handfish <- ifelse(handfishdata2$Juvenile=='FALSE','red','green')
col.handfish
```

```{r}
plot(Sighted_Depth_m ~ Fish_Length_mm, data = handfishdata2,
     xlab = 'Fish length (mm)', 
     ylab = 'Sighted depth (m)',
     main = 'Fish length & sighted depth of handfish',
     pch = 19, cex=2,
     col = scales::alpha(col.handfish, 0.3))

legend(x="bottomright", pch= 19, cex=0.7, legend = c("Juvenile","Adult"), col=levels(as.factor(scales::alpha(col.handfish, 0.2))))
```

  Now we try using boxplot to demonstrate the distribution of the variables.
  The unit of the y-axis would be interpreted as "mm" for "Fish length" and "m" for "Sighted depth".
# Boxplot handfishdata2 using "Fish_Length_mm" & "Sighted_Depth_m".
```{r}
boxplot(handfishdata2$Fish_Length_mm,handfishdata2$Sighted_Depth_m, names = c("Fish length", "Sighted depth"), main = "Handfish length & sighted depth")

```

  Now let's use Histogram to have a alternative view on the size distribution of the Spotted handfish from the data we have.
```{r}
hist(handfishdata2$Fish_Length_mm, 
     xlab = "Length of Handfish",
     main = NA)
```

  And the depth they were sighted.
```{r}
hist(handfishdata2$Sighted_Depth_m, 
     xlab = "Sighted depth",
     main = NA)
```

Lastly, we use the "cor.test" to get the p-value of Fish_Length_mm & Sighted_Depth_m.
We got a p-value of 0.000295, indicating a significant different in correlation between the 2 variables.
```{r}
cor.test(handfishdata2$Fish_Length_mm, handfishdata2$Sighted_Depth_m)
```
With a view using Linear Model, plotting the best linear regression result for the data. Also a better view of how the data is distributed. 
```{r}
ggplot(handfishdata2, aes(x = Fish_Length_mm, y = Sighted_Depth_m)) +
  geom_point(aes(fill=Juvenile),shape = 21, size=5) +
  stat_smooth(method = "lm", col = "blue")
```


  The depth distributions of Spotted handfish did not varied between adults and juveniles, but rather that most individuals preferred the depth of at least 6m or deeper before declining in number when the depth reached 11m deep.

  To conclude the hypothesis I proposed - "Adults/larger individuals tend to inhabit deeper water in comparison to juveniles/smaller individuals" was proven to be invalid as sorting and plotting of the raw distribution data of the Spotted handfish turned out to be none-relative. Fish length did not correspond to their sighted depth, meaning that juveniles do not get direct benefits from more shallow water, so nursey water does not exist, and that juveniles would distribute around nature habitats among adults.
Spotted handfish are endangered species due to their low population and vulnerable nature under the stress of predation from invasive seastars or destruction of natural habitats due to pollution or seabed scouring from boats' mooring chains/anchors. Still more precaution and preservation work would be needed to be put into the protection of these peculiar yet fascinating walking sea goblins.



Referrence:
1. https://portal.aodn.org.au/search
2. https://australian.museum/learn/animals/fishes/spotted-handfish-brachionichthys-hirsutus-lacepede-1804/
3. https://www.threatenedspecieslink.tas.gov.au/Pages/Spotted-Handfish.aspx
4. https://vianneydenis.github.io/OCEAN5098/df4810487c8a45838b57b12f305a2529def7225f/mapping.html#basic-map




2023/12/20 R Final Report
Hsiao-Yang Chu
